Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-29 Ben_Manuscripts/structure_paper/Draft.tex
updates
reworked intro

  %MRS14: I feel this introduction spends a bit too much time talking at too general a level.  The paper introduction to the problem tackled in the paper.  One simple way to tighten it up would be to improve the connection between the thesis and the data.  You say that highly selective membranes would be useful, but then don't provide evidence that they are the solution to the problems listed. 
  More highly selective membranes would be extremely useful for both the
  recovery of valuable dissolved species from and the purification of complex
  aqueous solutions. The supply of fresh water is being increasingly strained
  by population growth, industrialization and climate change
  \cite{elimelech_future_2011}. Consequently, people are turning towards
  treatment of unconventional water sources such as seawater and wastewater. 
  In addition to obtaining fresh water from them, these water sources, 
  particularly municipal and industrial wastewater, have been found to contain 
  valuable resources which can be separated using highly selective membranes~\cite{sales_resource_2015}.

  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane 
  filtration processes that can be used to separate solutes on the order of 1 
  nm in size and smaller, as well as ions. Both apply hydraulic pressure to 
  the feed solution in order to overcome osmotic pressure and force water
  and unfiltered components through the membrane. RO membranes typically have
  a thin film composite architecture which, at minimum, consists of a porous
  support layer and a dense polymer active layer. Separation occurs based on the differences in
  solubility and diffusivity of feed solution constituents 
  %MRS14:
  %with respect to the
  in the 
  active layer. Nanofiltration membranes have explicit pores on the order of 1
  nm in diameter which are typically tortuous and polydisperse in size. They 
  separate primarily based on size exclusion as well as Donnan exclusion if the
  membrane has a surface charge~\cite{van_der_bruggen_review_2003}.

  %MRS14: is selectivity towards water important, or selectivity against what one wants filtered out?
  The energy consumed during the purification of seawater and wastewater 
  using RO and NF membranes can be reduced by increasing their selectivity 
  towards water \cite{werber_materials_2016}. While researchers often focus on
  improving membrane permeability, the flux of water through a given membrane,
  it has been shown that increased water permeability only slightly decreases
  energy requirements \cite{cohen-tanugi_quantifying_2014}.
%  since the main energy requirement for a membrane separation is that needed
%  to create the hydraulic pressure necessary in order to overcome the 
%  osmotic pressure of the feed solution\cite{cohen-tanugi_quantifying_2014}. 
  Often times, multiple membrane passes are required in order to sufficiently
  %MRS14: not sure the boric acid part is that relevant, since we don't really talk about 
  %that in the rest of the paper.
  reduce contaminant levels. For example, boric acid is toxic to humans and 
  is present in seawater at levels well above acceptable drinking standards.
  It is difficult to sufficiently separate boric acid in a single pass, meaning
  multiple passes are needed and energy requirements nearly double \cite{fritzmann_state---art_2007}.
%  This is necessary in the case where high-purity water
%  is needed \cite{singh_production_2009}, when separating small neutral solutes \cite{ozaki_rejection_2002} or
%  when removing boric acid from seawater \cite{fritzmann_state---art_2007}.  
  The most effective way to reduce energy consumption
  would be to reduce the number of membrane passes for a given system using 
  more selective membranes. 
%   More highly selective membranes have the potential
%  to reduce the number of membrane passes in addition to eliminating the need 
%  for other post-treatment steps necessitated by incomplete separations.
  %dissolved species which negatively
%  affect human health.

  Not only will increased selectivity reduce the energy consumption of membrane
  processes, but it offers a way to recover valuable resources from the feed 
  streams. Municipal and industrial wastewaters are contaminated by harmful
  micropollutants, but also contain valuable dissolved solutes. Micropollutants include
  pharmaceutical and personal care products, hormones, pesticides and industrial
  chemicals, all of which have adverse effects on human health even at low 
  concentrations\cite{schwarzenbach_challenge_2006}. A selective membrane has the % There is a need for membranes
  potential to reject these components while still allowing the passage of valuable 
  resources for further processing and recovery.

  Municipal wastewaters are rich in carbon, nitrogen and phosphorus-containing 
  compounds. The recovery of such products, which can be achieved using a 
  selective membrane, has numerous potential uses \cite{sales_resource_2015}. 
  For example, nitrogen and phosphorus recovery can help sustain fertilizer 
  production which will help meet global food demand as population continues
  to increase \cite{xie_membrane-based_2016}.

  %MRS14: could possibly be food details, if selective membranes are the key to purifying industrial waste waters. 
  Industrial waste-waters are often quite complex with up to six times more 
  total dissolved solids than seawater\cite{werber_materials_2016}. For example, flowback water, produced
  during hydraulic fracturing of shale formations consists of relatively high
  concentrations of salts, metals, and soluble organic compounds. The majority
  of this water is disposed through deep well injection, however there is a growing public concern about
  its management which has prompted the use of separation technologies such as 
  RO and NF in order to reduce the volume of contaminated water~\cite{gregory_water_2011}.
  Some of the dissolved organic compounds in flowback water, such as acetate, 
  are potentially valuable and can be recovered with highly selective membranes
  ~\cite{dischinger_application_2017}.

@@

  Current commercial RO and NF membranes suffer limitations to their selectivity
  because their structures incorporate some degree of randomness. Although scalable, their 
  fabrication involves the spontaneous assembly of polymers into disordered structures
  which offer separation pathways that are tortuous and polydisperse in size 
  \cite{werber_materials_2016}. Tortuosity increases the effective length that a 
  solute must travel, while polydispersity limits membrane selectivity.

@@

  Selective separation by a semipermeable membrane barrier is a function of the
  geometric and chemical interactions of solutes with the membrane material. A
  molecule's size, shape, charge and polarity combine to determine the degree to
  which a solute partitions into a membrane and how fast it travels through the
  membrane. To separate a component from a mixture, one must understand how to
  design membranes in order to tune the relative transport rates of desired and
  undesired solutes\cite{gin_polymerized_2008,wijmans_solution-diffusion_1995}.

>>>>

  %MRS14: I feel this introduction spends a bit too much time talking at too general a level.  The paper introduction to the problem tackled in the paper.  One simple way to tighten it up would be to improve the connection between the thesis and the data.  You say that highly selective membranes would be useful, but then don't provide evidence that they are the solution to the problems listed.

  % In order to perform complex separations x, y and z at reduced costs, we need highly selective membranes 
  % include all descriptions of separation processes into this paragraph

  More highly selective nanoporous membranes would be extremely useful in order
  to perform complex aqeuous separations with seawater and various sources of
  wastewater. Sodium chloride and boron in seawater, and organic micropollutants
  found in municipal and industrial wastewaters are a few examples of the
  diversity of components that make up various water sources. By efficiently
  separating contaminants from feed solutions with highly selective membranes,
  one can reduce the number of required membrane passes and post-treatment steps,
  thus lowering the energy requirements of the separation processes.
  Additionally, one can extract valuable resources from the feed streams. For
  example, flowback water produced during hydraulic fracturing of shale
  formations contains dissolved species such as acetate whose extraction could be
  economically valuable.

% More highly selective membranes would be extremely useful for both the
% recovery of valuable dissolved species from and the purification of complex
%  aqueous solutions. The supply of fresh water is being increasingly strained
%  by population growth, industrialization and climate change
%  \cite{elimelech_future_2011}. Consequently, people are turning towards
%  treatment of unconventional water sources such as seawater and wastewater. 
%  In addition to obtaining fresh water from them, these water sources, 
%  particularly municipal and industrial wastewater, have been found to contain 
%  valuable resources which can be separated using highly selective membranes~\cite{sales_resource_2015}.
  % make possible with selectively permeable membranes -- better than thermal distillation

 % (2) existing nanoporous membranes + drawbacks

  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
  filtration processes that can be used to separate solutes on the order of 1 nm
  in size and smaller, as well as ions, however the porous architecture of
  commercially dominant membranes lack uniformity which severely impacts their
  selectivity. Although scalable, their fabrication involves the spontaneous
  assembly of polymers into disordered structures which offer separation pathways
  that are tortuous and polydisperse in size \cite{werber_materials_2016}.
  Tortuosity increases the effective length that a solute must travel, while
  polydispersity limits membrane selectivity.

  % (3) justification for why nanostructured membranes are a good idea for this
  % long-term route towards highly selective membranes are those that are nanostructured
  Nanostructured porous membrane materials have become increasingly popular for
  aqueous separations applications because they offer the ability to control pore
  architecture at the molecular scale, thereby permitting the design of
  solute-specific separation membranes \cite{humplik_nanostructured_2011},
  however their development has been limited by the ability to synthesize and
  scale various fundamentally sound technologies. Graphene sheets are atomically
  thick which results in excellent water permeability but defects during
  manufacturing severely impact selectivity \cite{cohen-tanugi_multilayer_2016}.
  Molecular dynamics (MD) simulations of carbon nanotubes show promise
  \cite{humplik_nanostructured_2011}, but synthetic techniques are unable to
  achieve scalable alignment and pore monodispersity
  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Consequently, there is a
  need for a scalable nanostructured porous membrane.

%BJC14: zeolites aren't really nanostructured
% Zeolites have sub-nm
%  pores with a narrow pore size distribution, and MD simulations of these
%  materials show that they exhibit complete rejection of solvated ions
%  \cite{murad_molecular_1998}- however, experimental rejection was low and
%  attributed to interstitial defects formed during membrane synthesis
%  \cite{li_desalination_2004}.

  % (4) justify LLCs

  % (5) justify need for simulations

%  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
%  filtration processes that can be used to separate solutes on the order of 1 nm
%  in size and smaller, as well as ions. Both apply hydraulic pressure to the feed
%  solution in order to overcome osmotic pressure and force water and unfiltered
%  components through the membrane. RO membranes typically have a thin film
%  composite architecture which, at minimum, consists of a porous support layer
%  and a dense polymer active layer. Separation occurs based on the differences in
%  solubility and diffusivity of feed solution constituents in the active layer.
%  Nanofiltration membranes have explicit pores on the order of 1 nm in diameter
%  which are typically tortuous and polydisperse in size. They separate primarily
%  based on size exclusion as well as Donnan exclusion if the membrane has a
%  surface charge~\cite{van_der_bruggen_review_2003}.

  %MRS14: is selectivity towards water important, or selectivity against what one wants filtered out?
%  The energy consumed during the purification of seawater and wastewater 
%  using RO and NF membranes can be reduced by increasing their selectivity 
%  towards water \cite{werber_materials_2016}. While researchers often focus on
%  improving membrane permeability, the flux of water through a given membrane,
%  it has been shown that increased water permeability only slightly decreases
%  energy requirements \cite{cohen-tanugi_quantifying_2014}.
%  since the main energy requirement for a membrane separation is that needed
%  to create the hydraulic pressure necessary in order to overcome the 
%  osmotic pressure of the feed solution\cite{cohen-tanugi_quantifying_2014}. 
%  Often times, multiple membrane passes are required in order to sufficiently
  %MRS14: not sure the boric acid part is that relevant, since we don't really talk about 
  %that in the rest of the paper.
%  reduce contaminant levels. For example, boric acid is toxic to humans and 
%  is present in seawater at levels well above acceptable drinking standards.
%  It is difficult to sufficiently separate boric acid in a single pass, meaning
%  multiple passes are needed and energy requirements nearly double \cite{fritzmann_state---art_2007}.
%  This is necessary in the case where high-purity water
%  is needed \cite{singh_production_2009}, when separating small neutral solutes \cite{ozaki_rejection_2002} or
%  when removing boric acid from seawater \cite{fritzmann_state---art_2007}.  
%  The most effective way to reduce energy consumption
%  would be to reduce the number of membrane passes for a given system using 
%  more selective membranes. 
%   More highly selective membranes have the potential
%  to reduce the number of membrane passes in addition to eliminating the need 
%  for other post-treatment steps necessitated by incomplete separations.
  %dissolved species which negatively
%  affect human health.

%  Not only will increased selectivity reduce the energy consumption of membrane
%  processes, but it offers a way to recover valuable resources from the feed 
%  streams. Municipal and industrial wastewaters are contaminated by harmful
%  micropollutants, but also contain valuable dissolved solutes. Micropollutants include
%  pharmaceutical and personal care products, hormones, pesticides and industrial
%  chemicals, all of which have adverse effects on human health even at low 
%  concentrations\cite{schwarzenbach_challenge_2006}. A selective membrane has the % There is a need for membranes
%  potential to reject these components while still allowing the passage of valuable 
%  resources for further processing and recovery.

%  Municipal wastewaters are rich in carbon, nitrogen and phosphorus-containing 
%  compounds. The recovery of such products, which can be achieved using a 
%  selective membrane, has numerous potential uses \cite{sales_resource_2015}. 
%  For example, nitrogen and phosphorus recovery can help sustain fertilizer 
%  production which will help meet global food demand as population continues
%  to increase \cite{xie_membrane-based_2016}.

  %MRS14: could possibly be food details, if selective membranes are the key to purifying industrial waste waters. 
%  Industrial waste-waters are often quite complex with up to six times more 
%  total dissolved solids than seawater\cite{werber_materials_2016}. For example, flowback water, produced
%  during hydraulic fracturing of shale formations consists of relatively high
%  concentrations of salts, metals, and soluble organic compounds. The majority
%  of this water is disposed through deep well injection, however there is a growing public concern about
%  its management which has prompted the use of separation technologies such as 
%  RO and NF in order to reduce the volume of contaminated water~\cite{gregory_water_2011}.
%  Some of the dissolved organic compounds in flowback water, such as acetate, 
%  are potentially valuable and can be recovered with highly selective membranes
%  ~\cite{dischinger_application_2017}.

@@

%  Current commercial RO and NF membranes suffer limitations to their selectivity
%  because their structures incorporate some degree of randomness. Although scalable, their 
%  fabrication involves the spontaneous assembly of polymers into disordered structures
%  which offer separation pathways that are tortuous and polydisperse in size 
%  \cite{werber_materials_2016}. Tortuosity increases the effective length that a 
%  solute must travel, while polydispersity limits membrane selectivity.

@@

%BJC14: probably unnecessary?
%  Selective separation by a semipermeable membrane barrier is a function of the
%  geometric and chemical interactions of solutes with the membrane material. A
%  molecule's size, shape, charge and polarity combine to determine the degree to
%  which a solute partitions into a membrane and how fast it travels through the
%  membrane. To separate a component from a mixture, one must understand how to
%  design membranes in order to tune the relative transport rates of desired and
%  undesired solutes\cite{gin_polymerized_2008,wijmans_solution-diffusion_1995}.
